Implicit yaddayadda

### 2011-09-27 papers/PLDI2012/implicitization.tex
petites modifs
Make sure math formula isn't cut before a )

\section{Bases}
\subsection{Static analysis by abstract interpretation}
Let $X$ be the set of possible states of the program variables; for instance, if the program has 3 unbounded integer variables, then $X = \ZZ^3$. The set $\parts{X}$ of subsets of $X$, partially ordered by inclusion, is often referred to as the \emph{concrete domain}. An \emph{abstract domain} is a set $\abstr{X}$ equipped with a partial order $\sqsubseteq$; for instance, it can be the domain of convex polyhedra in $\QQ^3$ ordered by geometric inclusion. In this article, all abstract domains are supposed to contain machine-representable objects, and all $\sqsubseteq$ order relations are supposed to be decidable.
The concrete and abstract domains are connected by a monotone \emph{concretization} function $\gamma: (\abstr{X},\sqsubseteq) \rightarrow (\parts{X},\subseteq)$: an element $\abstr{x} \in \abstr{X}$ represents a set $\gamma(\abstr{x})$.%
%
\footnote{%
Some presentations of abstract interpretation identify an element $\abstr{x}$ with the set of states $\gamma(\abstr{x})$ that it represents. This leads to simpler notations, but may also confuse if, as in some of our constructions, there exist several $\abstr{x}$ with identical $\gamma(\abstr{x})$, but distinct algorithmic behaviors.}

@@

We revise the rate limiter described in \ref{subsec:rate_lim}. In this example,
\emph{Path-focused} technique works well because all the paths starting at the
loop header are actually self loops. In such a case, the technique performs a
widening/narrowing sequence or accelerates the loop, thus leading to a precise
invariant. However, in real cases, there also exist paths that are not
self loops, and \emph{Path-focusing} only performs a widening. 
This widening may induce unrecoverable loss of precision.

>>>>

\section{Bases}
\subsection{Static analysis by abstract interpretation}
Let $X$ be the set of possible states of the program variables; for instance, if the program has 3 unbounded integer variables, then $X = \ZZ^3$. The set $\parts{X}$ of subsets of $X$, partially ordered by inclusion, is often referred to as the \emph{concrete domain}. An \emph{abstract domain} is a set $\abstr{X}$ equipped with a partial order $\sqsubseteq$; for instance, it can be the domain of convex polyhedra in $\QQ^3$ ordered by geometric inclusion. In this article, all abstract domains are supposed to contain machine-representable objects, and all $\sqsubseteq$ order relations are supposed to be decidable.
The concrete and abstract domains are connected by a monotone \emph{concretization} function $\gamma: \left(\abstr{X},\sqsubseteq\right) \rightarrow (\parts{X},\subseteq)$: an element $\abstr{x} \in \abstr{X}$ represents a set $\gamma(\abstr{x})$.%
%
\footnote{%
Some presentations of abstract interpretation identify an element $\abstr{x}$ with the set of states $\gamma(\abstr{x})$ that it represents. This leads to simpler notations, but may also confuse if, as in some of our constructions, there exist several $\abstr{x}$ with identical $\gamma(\abstr{x})$, but distinct algorithmic behaviors.}

@@

We revise the rate limiter described in \ref{subsec:rate_lim}. In this example,
\emph{Path-focused} technique works well because all the paths starting at the
loop header are actually self loops. In such a case, the technique performs a
widening/narrowing sequence or accelerates the loop, thus leading to a precise
invariant. However, in real cases, there also exist paths that are not
self loops, where \emph{Path-focusing} only performs a widening. 
This widening may induce unrecoverable loss of precision.
